---
title: "bootstrap"
author: "Yuqi Miao"
date: "11/14/2019"
output: html_document
---
# slides
1. bootstrap

Idea is to mimic repeated sampling with the one sample you have

Your sample is draw at random from your population

– You’d like to draw more samples, but you can’t
– So you draw a bootstrap sample from the one sample you have
– The bootstrap sample has the same size as the original sample, and is
drawn with replacement
– Analyze this sample using whatever approach you want to apply
– Repeat

```{r}
library(tidyverse)
library(modelr)
library(broom)
library(p8105.datasets)
set.seed(1)

##
```

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

```

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") ## 加ID！

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```


## fit 2 model

```{r}
sim_df_const %>% 
    lm(y~x,data =.) %>% 
    broom::tidy()
sim_df_nonconst %>% 
    lm(y~x,data =.) %>% 
    broom::tidy()
# non_const a little bigger than const?
```

## bootstrap
write a function to draw a bootstrap sample based on a data frame

resample:

```{r}
sim_df_const %>% 
    sample_frac(size=1,replace = FALSE) %>% 
    arrange(x)

## bootstrap
sim_df_nonconst %>% 
    sample_frac(size=1,replace = TRUE) %>% 
    arrange(x)
```

```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```


## organize a dataframe

```{r}
boot_straps = tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000,boot_sample(df = sim_df_nonconst))
)

## replace sample 1000 times
```

Do some kind of analysis

```{r}
bootstraps_results = boot_straps %>% 
    mutate(
        models = map(strap_sample,~lm(y~x,data = .x)),
        results = map(models, broom::tidy)
    ) %>% 
    select(-strap_sample,-models) %>% 
    unnest()

```

## summarise the results

```{r}
bootstraps_results %>% 
    group_by(term) %>% 
    summarise(se = sd(estimate))
```



## try modelr package


one step to finish the replacement sampling

```{r}
boot_straps = 
    sim_df_nonconst %>% 
    modelr::bootstrap(1000)
    
```

## What if your assumptions are wrong?

```{r}
sim_df_const %>% 
    lm(y~x, data =.) %>% 
    broom::tidy()

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))

```

reusable model chunk

```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```


## boot_strap?? size = 1


```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```



```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```


```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```

本质上，Bootstrap方法，是将一次的估计过程，重复上千次上万次，从而便得到了得到上千个甚至上万个的估计值，于是利用这不止一个的估计值，我们就可以估计[公式]均值以外的其他统计量：比如标准差、中位数等

confidence interval:







